\documentclass{beamer}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{mathtools}


%Information to be included in the title page:
\title{Presentation for the Quantum Seminar}
\author{Jos\'e Manuel Rodr\'iguez Caballero}
\institute{University of Tartu}
\date{Spring 2020}



\begin{document}

\frame{\titlepage}

\begin{frame}{Subject}
My presentation is about the paper\footnote{I will not repeat the notation from the paper in this presentation. If someone needs a clarification, either read the paper or ask me during the presentation.}:
$\newline$

\begin{quote}
Bouman, Niek J., and Serge Fehr. "Sampling in a quantum population, and applications." Annual Cryptology Conference. Springer, Berlin, Heidelberg, 2010.
\end{quote}

My presentation may differ in some points with respect of the presentation given by the authors.

\end{frame}

\begin{frame}{Contributions of the paper}
\begin{flushleft}

\textbf{Contribution 1.} The authors introduce a framework in for \textit{sampling quantum population}.
$\newline$

\textbf{Contribution 2.} This framework is used in a new proof of the security of the \emph{quantum key distribution protocol BB84} (entanglement-based version).
$\newline$

\textbf{Contribution 3.} This framework is used in a new proof of the security of the \emph{quantum oblivious-transfer from bit-commitment}.

\end{flushleft}
\end{frame}

\begin{frame}
\begin{center}
\Large{\textbf{Presentation of Contribution 1.} }\normalsize
$\newline$
\end{center}

\begin{flushleft}
The authors introduce a framework in for \textit{sampling quantum population}.
\end{flushleft}
\end{frame}

\begin{frame}{Overview of Contribution 1}

The authors define a \emph{sampling and estimation strategy} (\emph{sampling strategy} for short). This strategy can be used in order to study both classical and quantum populations. The ``quantum error" is bounded by the square root of the ``classical error", thus reducing the quantum information-theoretical problem to a well-studied probabilistic problem.
\end{frame}

\begin{frame}{Sampling strategy}
Let $n$ be a positive integer, $\mathcal{A}$ be a finite alphabet and $\mathcal{S}$ be a finite set of seeds. Assume that $|\mathcal{A}| \geq 2$ and $|\mathcal{S}| \geq 1$. A \emph{sampling strategy} is a triplet $\left( P_T, P_S, f \right)$, where $P_T$ is a probability distribution over $\mathcal{T} := 2^{[n]}$, $P_S$ is a probability distribution over $\mathcal{S}$ and $f$ is a real-valued function defined on the finite set\footnote{The notation $\mathcal{A}^{\ast}$ is for the free monoid over $\mathcal{A}$.}
$$
\textrm{Dom}_f := \left\{ (t, q, s)\in \mathcal{T}\times \mathcal{A}^{\ast} \times \mathcal{S}: \quad |t| = |q| \right\}.
$$
$\newline$
Remark. The number of degrees of freedom of a sampling strategy is finite and it is asymptotically equivalent to $|\mathcal{S}|^2 \, \left( 2| \mathcal{A} | + 2 \right)^n$ as $n\to\infty$.
\end{frame}

\begin{frame}
\begin{center}
\Large{Classical populations}
\end{center}
\end{frame}

\begin{frame}{What is a classical population?} 
In the context of the paper, a \emph{classical population} is a finite word $q$ over the alphabet $\mathcal{A}$. The alphabet $\mathcal{A}$ contains a distinguished element, that we will denote by $0$. We are interested in estimating how many letters in $q$ are different from $0$, i.e., the Hamming weight of $q$. In order to simplify the presentation, we will use the relative hamming weight of $q$, denoted $\omega(q)$, which is the Hamming weight of $q$ divided by its length.
\end{frame}


\begin{frame}{Example of classical population} 
The classical population could  be the population of the People's Republic of Wakanda\footnote{I am considering an idealized situation, in order to avoid all the complications of the a real-life scenario, e.g., fake data and heterogeneous properties of the population. In Wakanda everything will be as homogeneous as possible.} (each person corresponds to a position in the word $q$) and the alphabet could be $\mathcal{A} = \{0, 1\}$, where $0$ and $1$ stand for  uninfected and infected of COVID-19, respectively. In order to estimate how many people are infested with COVID-19, we will study a random sample of the population, which will be small in comparison to the size of the population. Finally, we will extrapolate the data from the sample to the whole population.
\end{frame}

\begin{frame}{How to estimate?} 
Given a sampling strategy $\left(P_T, P_S, f \right)$ and a classical population $q = q_1 q_2 q_3 ... q_n \in \mathcal{A}^n$. We take a random pair $(t, s) \in \mathcal{T} \times \mathcal{S}$ (using the joint distribution of $P_T$ and $P_S$). Let
$$
\tau_1 < \tau_2 < ... < \tau_{k}
$$
be the elements of $t$ written in increasing order. Let
$$
\overline{\tau }_1 < \overline{\tau}_2 < .... < \overline{\tau}_{n-k}
$$
be the elements of $[n]\backslash t$ written in increasing order. We define
$$
q_t = q_{\tau_1} q_{\tau_2} ... q_{\tau_k}, \quad q_{\overline{t}} = q_{\overline{\tau}_1} q_{\overline{\tau}_2} ... q_{\overline{\tau}_{n-k}}.
$$

By definition, we \emph{estimate} that the relative Hamming weight of $q_{\overline{t}}$ is given by $f\left(t, q_t, s\right)$.
\end{frame}

\begin{frame}{Example of estimation} 
Let's return to the example of the population of Wakanda, identified with the word $q$. We define $\mathcal{S} = \{\perp\}$, i.e., we do not use a random seed, here. So, $P_S$ is trivially the uniform distribution on $\mathcal{S}$. Now, let assume that $P_T$ is the uniform distribution on $\mathcal{T}$, i.e., $P_T(t) = \frac{1}{2^n} \left(\!\!\! \begin{array}{c} n \\ |t| \end{array} \!\!\!\right)$. Finally, define $f(t, q, s) := \omega(q)$.
$\newline$

This sampling strategy is just a formalization of the heuristic approach assuming that the frequency of cases of COVID-19 in the whole population is the same as in our uniformly random sample. This is not necessarily the case in reality, e.g., people working in hospitals have a higher probability of getting infested than the remain of the population.
\end{frame}

\begin{frame}{Set of classical $\delta$-close states} 
Let $\delta$ be a positive real number. We define the  \emph{set of classical $\delta$-close states} as
$$
B_{t,s}^{\delta} := \left\{ q\in\mathcal{A}^n: \quad \left| \omega\left(q_{\overline{t}}\right) - f\left(t, q_t, s\right) \right| <  \delta \right\},
$$

Heuristic idea: for $\delta$, $t$ and $s$ fixed, the larger the set $B_{t,s}^{\delta}$ is, the better the function $f$ is for estimation (with respect to $t$ and $s$).
\end{frame}

\begin{frame}{Example of set of classical $\delta$-close states} 
In Wakanda example, $B_{t,s}^{\delta}$ is the set of all possibilities (after choosing $t$ and $s$) in which the frequency of infection of COVID-19 in the sample is $\delta$-close to the frequency of infection in the remaining part of the population of Wakanda.
\end{frame}

\begin{frame}{Random set of classical $\delta$-close states} 
Let $T$ and $S$ be random variables associated to the probability distributions $P_T$ and $P_S$ respectively. Notice that the pair $(T, S)$ is a random variable. Furthermore, the evaluation of $(t,s) \mapsto B_{t,s}^{\delta}$ at $(T,S)$ determines a random variable, denoted $B_{T,S}^{\delta}$ and associated to the probability distribution
$$
\textrm{Pr}\left[ B_{T,S}^{\delta} \in \Gamma \right] := \textrm{Pr}\left[ (T, S) \in \left\{(t,s)\in\mathcal{T}\times\mathcal{S} :\quad B_{t,s}^{\delta} \in \Gamma\right\} \right]
$$
where $\Gamma\subset 2^{\mathcal{A}^n}$. The call $B_{T,S}^{\delta}$ the \emph{random set of classical $\delta$-close states}.
$\newline$

Heuristic idea: for $\delta$ fixed, the ``larger" the random set $B_{T,S}^{\delta}$ is, the better the strategy is for estimation.
\end{frame}

\begin{frame}{Example of random set of classical $\delta$-close states} 
In Wakanda example, $B_{T,S}^{\delta}$ is the random set of all possibilities (before choosing $t$ and $s$) in which the frequency of infection of COVID-19 in the sample is $\delta$-close to the frequency of infection in the remaining part of the population of Wakanda.
\end{frame}

\begin{frame}{Cl assical $\delta$-error} 

The \emph{classical $\delta$-error} is defined as
$$
\varepsilon_c^{\delta} :=\max_{q\in\mathcal{A}^n} \textrm{Pr}\left[ B_{T,S}^{\delta} \in \left\{X\in 2^{\mathcal{A}^n}: \quad q \not\in X \right\}\right].
$$

Heuristic idea: $\varepsilon_c^{\delta}$ measures the probability that the sampling strategy fails in the worst-case scenario\footnote{Notice that the expression inside the bracket is equivalent to $q \not\in B_{T,S}^{\delta}$.}.
\end{frame}

\begin{frame}{Example of classical $\delta$-error} 
In Wakanda example, $\varepsilon_c^{\delta}$ is the largest probability, with respect to all possible populations, that the frequency of infection of the sample is not $\delta$-close to the frequency of infection of the remaining part of the population of Wakanda.
\end{frame}


\begin{frame}
\begin{center}
\Large{Quantum populations}
\end{center}
\end{frame}


\begin{frame}
\begin{center}
\Large{\textbf{Presentation of Contribution 2.} }\normalsize
$\newline$
\end{center}

\begin{flushleft}
This framework is used in a new proof of the security of the \emph{quantum key distribution protocol BB84} (entanglement-based version).
\end{flushleft}
\end{frame}

\begin{frame}
\begin{center}
\Large{\textbf{Presentation of Contribution 3.} }\normalsize
$\newline$
\end{center}

\begin{flushleft}
This framework is used in a new proof of the security of the \emph{quantum oblivious-transfer from bit-commitment}.
\end{flushleft}
\end{frame}

\begin{frame}
\begin{center}
\Large{\textbf{End of my presentation} }
\end{center}
\end{frame}

\end{document}